---
title: 'Using R to analyse additive designs'
author: "Maxwel C Oliveira, Gustavo AM Pereira, Evander A Ferreira, José B Santos, Stevan Z Knezevic, and Rodrigo Werle"
date: "January 24, 2018"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

*Supporting Information* of manuscript **Additive design: the concept and data analysis**, [Weed Research](https://onlinelibrary.wiley.com/journal/13653180).

Correspondence: Maxwel Coura Oliveira, Department of Agronomy, University of Wisconsin-Madison, Madison, WI, USA 53506. Tel: (+1) 608-262-7130; E-mail: max.oliveira@wisc.edu, maxwelco@gmail.com


#Download R and Rstudio 
At <https://www.r-project.org/>, go to download in the left column, click in CRAN and select a location near you. For example, in Brazil, you can select seven different areas. Then download [**R**](https://www.r-project.org) compatible with your system (Linux, Mac or Windows). Once you have downloaded [**R**](https://www.r-project.org), you should also download [**RStudio**](https://www.rstudio.com). [**RStudio**](https://www.rstudio.com) is a friendly interface for programers. Scroll down to [**RStudio**](https://www.rstudio.com) and click on Download. Choose the free version of [**RStudio**](https://www.rstudio.com); there will also be [**RStudio**](https://www.rstudio.com) version for Linux, Mac, and Windows. 


#Create an Rstudio file
Open **RStudio** at the toolbar, click in the file, New Project…, Existing Directory, and choose the folder that contains your data. Your data file has to be in that selected folder. Also, we recommend your data to be saved as csv (comma delimited) file.

##Load the data in Rstudio
Assign the name of your data set (replace “DMT” to a name of your choice). If you use a comma (,) for separating decimals places, use *read.csv2()*. If you use a period (.), use *read.csv()*. In parentheses, write the name of your data set file. 

```{r LoadData, warning=F, include=TRUE}
DMT=read.csv("dmshoot.csv")
```


The command *head* prints the first six lines of the data set. It is useful for double checking your data.
```{r head, warning=F, include=TRUE}
head(DMT)
```


The command *str* prints how **RStudio** is reading the characters vector in a data set.
```{r str, warning=F, include=TRUE}
str(DMT)
```

#Rectangular hyperbola model

The empirical model:  $$Y=\frac{I * x}{ 1 + (\frac{I}{A})*x}$$ is the standard model to describe additive competition studies. *I* represents the slope of *Y* (yield loss) when *x* (weed density) approximate zero. Also, *A* is the asymptote or maximum expected yield loss (%).


##Step 1) Fit a full model, a rectangular hyperbola with 4 parameters

**Full** is a user-defined name that will contain all information about the fitted model generated by *nls* (nonlinear least squares) function. The *start* is used to estimate values of parameter *I* and *A* for the model. Parameters can determine from visual inspection of the data set (plotting data and observing trends). The brackets [weed] for each parameter in the equation tell **R** to estimate a parameter for each weed species (4 parameters).
```{r Full model, warning=F}
Full = nls(yl ~ (I[weed]*densityweed)/(1+(I[weed]/A[weed])*densityweed), data=DMT,
           start=list(I=c(60,30), A=c(80,60)), trace=T)
```

###Check estimated parameters
The *summary* command provides the estimated parameters *I* and *A* for each weed species, *Commelina benghalensis* (species 1) and *Richardia brasiliensis* (species 2).
```{r Fullparm, warning=F}
summary(Full)
```


##Step 2) Fit a reduced model (Red.1), rectangular hyperbola model with 2 parameters.
**Red.1** is a user-defined name that will contain information about the first reduced model generated by the *nls* function. Notice that we do not include bracket [weed] after each parameter *I* and *A*. In this case, we are combining parameter *I* and *A* for both weed species. We hypothesize that a single parameter *I* and *A* for both species is enough to describe the crop-weed relationship (e.g., no difference of *I* and *A* between species). 
```{r Red.1 model, warning=F}
Red.1 = nls(yl ~ (I*densityweed)/(1+(I/A)*densityweed), data=DMT, 
start=list(I=40, A=80), trace=T)
```

###Check estimated parameters
This command provides the estimated parameters *I* and *A* for both weed species combined.
```{r Red.1parm, warning=F}
summary(Red.1)
```


###Test the first hypothesis
Hypothesis testing using *ANOVA*. We test this hypothesis using the **Full** model (*I* and *A* for each species) to compare with **Red.1** (single *I* and *A* for both species). If P-value>0.05, models are similar; therefore we should use the **Red.1** model, which means that the simplest model (**Red.1**) is appropriate to describe crop-weed relationship. If not we should proceed to the next hypothesis.
```{r hyp1, warning=F}
anova(Full, Red.1)
```
The F-test showed P<0.05. Therefore the Red.1 model is not appropriate to describe the crop-weed relationship.


##Step 3) Fit a reduced model (Red.2), rectangular hyperbola model with 3 parameters
**Red.2** is a user-defined name that will contain information about the second reduced model generated by the *nls* function. Notice that the bracket [weed] is after the parameter *A* only, which means that we are testing a hypothesis of single parameter *I*, but different *A* for the species. 
```{r Red.2 model, warning=F}
Red.2 = nls(yl ~ (I*densityweed)/(1+(I/A[weed])*densityweed), data=DMT, 
            start=list(I=60, A=c(80,60)),  trace=T)
```

###Check estimated parameters
This command provides the estimated parameters *I* for both weed species and *A* for each weed species.
```{r Red.2parm, warning=F}
summary(Red.2)
```

###Test a second hypothesis
Hypothesis testing using F-test. We are using the Full model (separated I and *A* for each species) to compare with Red.2 (single *I* and different *A* for both species). If P-value>0.05, models are similar; therefore, we should use the **Red.2** model, which means that the simplest model (**Red.2**) is appropriate to describe crop-weed relationship. If not we should proceed to the next hypothesis.
```{r hyp2, echo=T, warning=F}
anova(Full, Red.2)
```
The F-test showed P<0.05. Therefore the Red.2 model is not appropriate to describe the crop-weed relationship.



##Step 4) Fit a reduced model (Red.3), rectangular hyperbola model with 3 parameters
Red.3 is a user-defined name that will contain information about the third reduced model generated by the *nls* function. Notice that the bracket [weed] is after the parameter *I* only, which means that we are testing a hypothesis of different parameter *I*, but single parameter *A* for the species.
```{r Red.3 model, warning=F}
Red.3 = nls(yl ~ (I[weed]*densityweed)/(1+(I[weed]/A)*densityweed), data=DMT,
            start=list(I=c(30,30), A=70), trace=T)
```

###Check estimated parameters
This command provides the estimated parameters *I* for each weed species and *A* for both weed species.
```{r Red.3parm, warning=F}
summary(Red.3)
```

###Test a third hypothesis
Hypothesis testing using F-test. We are using the Full model (separated *I* and *A* for each species) to compare with Red.3 (different *I* and single *A* for both species). If P-value>0.05, models are similar; therefore we should use the **Red.3** model, which means that the simplest model (**Red.3**) is appropriate to describe the crop-weed relationship.
```{r hyp3, warning=F}
anova(Full, Red.3)
```
Results showed that P >0.05. Therefore, the **Full** model can be simplified to **Red.3** model.

##Plotting the Red.3 model

###**Rstudio** basic figure

The command *par* is used to define the plot size.
The command *plot* and *lines* are used to generate the figure, and the averaged points of yield loss at each density (Fig. 5). The command *subset* is adding each weed species separately in the plot (weed 1) and lines (weed 2). 

The x is a user-defined name; it will contain the x-axis sequence of the data set. weed1 and weed2 is also a user-defined name, and this is the equation with the previous parameter estimates *I* and *A* estimated from Red.3 model using the nls function. Notice that the parameters estimated in Red.3 model were inserted in the rectangular hyperbola model for each weed species (Figure 1).


The command *lines* will insert the previous equation into the plot. Command *lty*, *lwd*, and *col* define the line type, size, and color, respectively.

The command *legend* will add the legend to the plot area.
```{r plot, warning=F, fig.cap="This figure is created with Rstudio basic commands and Red.3 model of the manuscript Additive design: the concept and data analysis."}
par(mar=c(5,6,2,2), mgp=c(3,1.5,0))
plot(yl~densityweed, data=DMT, subset = weed =="1", pch=16, cex=1, las=1, 
     xlab=expression("Weed Density (plants pot"^-1*")"), ylim=c(-10,110), 
     ylab = "Yield Loss (%)", cex.axis=1, cex.lab=1)
lines(yl~densityweed, type="p",data=DMT, subset = weed =="2", col=2, cex=1, pch=1)

x=seq(0,4,0.25)
weed1=(228.357*x)/(1+(228.357/106.170)*x)
weed2=(37.000*x)/(1+(37.000/106.170)*x)

lines(x,weed1, lty=1, lwd=1, col=1)
lines(x,weed2, lty=3, lwd=1, col=2)

legend("bottomright", legend=c("C. benghalensis", "R. brasiliensis"), text.font = 3, 
       col=c(1,2), pch= c(16,1), lty=c(1,3), lwd= c(1,1), bty="n", cex=1)
```



###High-quality figure in **Rstudio**

The package *ggplot2*, an excellent package for producing high-quality figures in **Rstudio**. 

```{r library, warning=F}
#install.packages("ggplot2")
#install.packages("broom")
library(ggplot2)
library(broom)
```


```{r Red model, warning=F}
DMT$weed<-factor(DMT$weed, levels=c("1", "2"), 
                 labels=c("Commelina benghalensis",
                          "Richardia brasiliensis"))


Red.3 = nls(yl ~ (I[weed]*densityweed)/(1+(I[weed]/A)*densityweed), data=DMT,
                      start=list(I=c(30,30), A=70), trace=T)
summary(Red.3)



nd1 = data.frame(densityweed=seq(0, 4, 0.01), weed="Commelina benghalensis")
nd2 = data.frame(densityweed=seq(0, 4, 0.01), weed="Richardia brasiliensis")
nd = rbind(nd1, nd2)

pred<- augment(Red.3, newdata=nd)
```

```{r Red model plot, fig.align="left", fig.cap="This is the Fig. 5 of the manuscript Additive design: the concept and data analysis. This Figure is created with package ggplot2 in Rstudio"}
ggplot(DMT, aes(x=densityweed, y=yl, color=weed)) + geom_point(shape=1, size=3) + 
  geom_line(data = pred, size=1.3, aes(x=densityweed, linetype=weed, y=.fitted)) +
  labs(fill="", y="Yield loss (%)", 
       x=expression(bold(paste("Weed density (plants pot"^"-2",")")))) +
  scale_colour_manual(values = c("red", "black"))+
  scale_y_continuous(limits=c(-25,110), breaks = c(-25,0,25,50,75,100)) +
    theme(axis.text=element_text(size=15, color="black"), 
        axis.title=element_text(size=17,face="bold"), 
        panel.background = element_rect(fill="white", color = "white"), 
        panel.grid.major = element_line(color = "white"), 
  panel.grid.minor = element_blank(), 
  panel.border = element_rect(fill=NA,color="black", size=0.5, 
  linetype="solid"), legend.position=c(0.7,0.15), 
  legend.text = element_text(size = 12, colour = "black", face="italic"), 
  legend.key = element_rect(fill=NA), legend.key.height  = unit(1.5, "line"),
  legend.key.width = unit(2.2, "line"),
legend.background = element_rect(fill =NA),  legend.title=element_blank())  + 
  ggsave("Red.tiff", units="in", width=4, height=4, dpi=300)
```

Notice that the figure is created with Red.3 model (rectangular hyperbola model) using *ggplot2* package (Figure 2). This is the Fig. 5 published in the manuscript **Additive design: the concept and data analysis**.



##AICc model selection and Goodness of fit

According to the AICc criterion, the top model has the lowest AICc value. The AICc calculation can be simplified using **R**, the first step is loading the package *AICcmodavg*.

```{r aic library}
library(AICcmodavg)
```


The four candidate models using the rectangular hyperbola are compared using AICc.
```{r aic table, warning=FALSE}
cand.mods<- list(Full, Red.1, Red.2, Red.3)
 
Modnames<- c('Full',' Red.1',' Red.2',' Red.3')

aictab(cand.set = cand.mods,modnames = Modnames, sort = TRUE)
```


Root mean square error (RMSE) for goodness of fit of the top model (**Red.3**) selected.
```{r assessing fit of top model, warning=FALSE}
mse <- mean(residuals(Red.3)^2/df.residual(Red.3))
rmse <- sqrt(mse)
rmse
```

##Obtaining the Confidence Internals for the Top model (Red.3)

It is needed the package *nlstools* and the command *confint2* to obtain the 95% confidence intervals for parameters *I* and *A* for the **Red.3**.
```{r Confidence Intervals, warning=FALSE}
#install.packages("nlstools")
library(nlstools)
confint2(Red.3, level=0.95)
```

#Extra - Setting a limit to the rectangular hyperbola parameters

Here we demonstrate how to set an upper limit to parameter *A* of **Red.3** model. Notice that we have to add *alg="port"* and *upper* command to the function. The *upper* command has three numbers, the first two set a limit of 10000 to parameter *I* of *R. brasiliensis* and *C. benghalensis*. The last *upper* number set a limit *A*=100%, which will lock the upper limit to a biologically meaningful value. 
 

```{r Red.3 limit model, warning=FALSE}
Red.3_lim = nls(yl ~ (I[weed]*densityweed)/(1+(I[weed]/A)*densityweed), data=DMT, 
                start=list(I=c(30,30), A=70), alg="port", 
                upper=c(10000, 10000, 100), trace=T)

summary(Red.3_lim)
```


#Acknowledgements
The statistical procedures are presented here with [**Rmarkdown**](https://rmarkdown.rstudio.com) and [**RStudio**](https://www.rstudio.com/).
  
  
  





